---
title: "PA1_template.Rmd"
output: html_document
---

Note: this document assumes that the R markdown file and the data are in the same directory, and that directory is set to the working directory (e.g., using `setwd()`).

## Load and process the data
First we read in the data from the csv file into a variable called `actdata`. Next we need to process the data:
1. To make a histogram of the number of steps taken each day and
2. To calculate and report the mean and median total number of steps taken per day
This wording is confusing to me. From reading the forums, I think we're asked to process the raw data to find the total number of steps each day. Then we are supposed to use that processed data to show a histogram of the number of steps taken each day, which would show a count of the number of days with 0-n steps, with n-2n, 2-3n, etc. Finally, we are supposed to use the processed data to find the mean and median number of daily steps.

```{r}
actdata <- read.csv("activity 2.csv")
daystats <- aggregate(steps ~ date, actdata, sum, na.rm = TRUE)
hist(daystats$steps, breaks = 10)
mean(daystats$steps)
median(daystats$steps)

```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
